Biotic invasions fuck with the manageability of pollination networks

### 2017-02-23 paper/supp_info_2.Rmd
Add statistical models table

>>>>

# Statistical models

```{r table-nd-coef, echo = FALSE, warning = FALSE, message = FALSE, results = "asis", sanitize = FALSE}
library(glmulti)

manag_table <- manag_models %>%
			coef.glmulti(select = 0.95) %>%
  as.data.frame() %>%
  tibble::rownames_to_column("factor") %>%
  dplyr::mutate(pare = grepl("(", factor, fixed =T),
                factor = plyr::mapvalues(factor, 
                												 c("studylopezaraiza", "invTRUE",
                												 	"I(n_links/(n_pla * n_pol))",
                												 	"I(n_pla + n_pol)", 
                												 	"I(n_pla/n_pol)"),
                												 c("study site", "invasion status",
                												 	"connectance", "spp. richness", 
                												 	"ratio plant/pollinator"))) %>%
  dplyr::arrange(-pare, -Importance, factor) %>% 
  dplyr::select(-pare) %>%
  magrittr::set_names(c(" ", "est.", "var", "mod.", "imp.", "C.I.")) %>%
			dplyr::select(-var, -mod.)

manag_table %>%
	xtable::xtable(caption = "\\textbf{Coefficients of the $n_D$ models}. Estimates are averaged over the models that accounted for 95\\% of the evidence weight.",
										 digits =  c(0, 0, 2, 2, 2),
										 display = c("d", "s", "f", "f", "G")) %>%
	print(booktabs = T, include.rownames = F,  caption.placement = "top", comment = F, sanitize.text.function = function(x){x})
